Uncertainty propagation in deep neural networks for sparse coding

### 2018-03-10 paper/BayesianLISTA.tex
minor fixes

\begin{abstract}
In the Bayesian neural network framework prior distributions are imposed on weights of a network and a posterior distribution of an output is inferred, rather than a point prediction provided by conventional neural networks. Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction. Uncertainty of the prediction is a result of weight uncertainty propagation through the layers of a network. We propose a novel method of propagating uncertainty through the soft thresholding nonlinearity. The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time. As an example we design a Bayesian Learned Iterative Shrinkage-Thresdholding Algorithm (Bayesian \textsc{lista}) network. We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation. A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and quantified estimates of uncertainty in these predictions.
\end{abstract}

@@

The soft thresholding function shifts elements that are greater than $\lambda$  or less than $-\lambda$ towards $0$. Let $\psi(\cdot)$ denote the density of the soft thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$. Then the first moment of $x^* \neq 0$ is:

>>>>

\begin{abstract}
In the Bayesian neural network framework prior distributions are imposed on weights of a network and a posterior distribution of an output is inferred, rather than a point prediction provided by conventional neural networks. Therefore, Bayesian neural networks estimate both an output for a test data and uncertainty of this prediction. Uncertainty of the prediction is a result of weight uncertainty propagation through the layers of a network. We propose a novel method of propagating uncertainty through the soft thresholding nonlinearity. The method expands the area of Bayesian neural networks and enables the soft thresholding nonlinearity to be included in Bayesian deep neural networks for the first time. As an example we design a Bayesian Learned Iterative Shrinkage-Thresholding Algorithm (Bayesian \textsc{lista}) network. We develop a highly efficient posterior inference algorithm based on probabilistic backpropagation. A series of experiments on sparse coding shows that the proposed framework provides both accurate predictions and quantified estimates of uncertainty in these predictions.
\end{abstract}

@@

The soft thresholding function shifts elements that are greater than $\lambda$  or less than $-\lambda$ towards $0$. Let $\psi(\cdot)$ denote the density of the soft-thresholded distribution on $x^* \neq 0$, $\phi(\cdot)$ denote the density of the original Gaussian distribution on $x$. Then the first moment of $x^* \neq 0$ is:
